Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-09 article.tex
Add hypothesis

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, epitopes, T lymphocyte, MHC-2

@@

\begin{itemize}
  \item $\mathcal{H}_1$: MHC-II binds as often to TMHs as the cytosolic and extracellular
    parts of a pathogen's transmembrane proteins
  \item $\mathcal{H}_2$: The TMHs of [a pathogen] have the same mutation rate 
    as the cytosolic and extracellular
    parts of its transmembrane proteins
\end{itemize}

>>>>

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, epitopes, T lymphocyte, MHC-2,
COVID-19

@@

\begin{itemize}
  \item $\mathcal{H}_1$: MHC-I has the same percentage of epitopes overlapping
    (that is 5.73 to 5.59 percent, with a confidence interval of 99 percent) 
    with TMHs in COVID-19 as in 
4 + ((117 / 135) * 2) = 5.73
4 + ((107 / 135) * 2) = 5.59

  \item $\mathcal{H}_2$: MHC-II binds as often to TMHs as the cytosolic and extracellular
    parts of a pathogen's transmembrane proteins
  \item $\mathcal{H}_3$: The TMHs of [a pathogen] have the same mutation rate 
    as the cytosolic and extracellular
    parts of its transmembrane proteins
\end{itemize}
